### 2012-10-10 Docs/MESA/hopper_compile.tex
renname docs Docs

There are several steps needed to compile {\sf MAESTRO} with {\sf MESA} on 
Hopper:
\begin{enumerate}
\item Edit the {\tt makefile\_header} in the {\tt utils} directory
\item Edit the {\tt build\_and\_test} script in the {\tt utils} directory
\item Edit the {\tt chem\_lib.f} file in the {\tt chem} directory
\item Edit the {\tt mtx} makefile
\item Edit the makefiles in {\tt screen}, {\tt utils}, {\tt num} and 
{\tt interp\_1d}
\item Edit the {\tt install} script in the main {\sf MESA} directory
\item Edit the {\tt BoxLib/Tools/F\_mk/GMakedefs.mak} makefile
\item Edit the {\tt BoxLib/Tools/F\_mk/comps/Linux\_cray.mak} file
\item Install {\sf MESA}
\item Compile {\sf MAESTRO}
\end{enumerate}

@@

  # must explicity define all compilation flags
  FCbasic = $(SPECIAL_FC_FLAGS)
  FCimpno = -eI
  FCchecks =
  FCwarn = -m 3
  FCfixed = -f fixed -N 132
  FCfixed72 = -f fixed -N 72
  FCfree = -f free
  FCopt = -O 1
  FCdebug = -g -O0
  FCstatic =

@@

The {\tt build\_and\_test} script in the {\tt utils} directory is 
responsible for compiling the main module directory as well as compiling 
and running the test directory. We want to turn off the compiling and 
running of the test directory to ensure that {\sf MESA} compiles successfully. 
A portion of the {\tt build\_and\_test} script looks like this:
\begin{lstlisting}[language=bash,mathescape=false]
  cd make
  make
  check_okay
  cd ../test
  ./mk
  check_okay
  if [ -x test_quietly ]
  then
          ./test_quietly
          check_okay
  fi
  ./ck >& diff.txt
\end{lstlisting}
we wish to change it to this:
\begin{lstlisting}[language=bash,mathescape=false]
  cd make
  make
  check_okay
  #cd ../test
  #./mk
  check_okay
  if [ -x test_quietly ]
  then
  #        ./test_quietly
          check_okay
  fi
  #./ck >& diff.txt
\end{lstlisting}
This disables the compiling and running of the test directory.

@@

Open the {\tt chem\_lib.f} file located in {\tt chem/public}. In the 
{\tt generate\_nuclide\_set} subroutine, the implied do loop must be removed 
and replaced with an actual do loop. For an unknown reason, the implied do 
loop was causing a Segmentation Fault on Hopper with the Cray compiler. The 
implied loop:
\begin{lstlisting}[language=fortran,mathescape=false]
  set = [(nuclide_set(names(i), i), i=1, size(names))]
\end{lstlisting}
should be changed to an explicit do loop:
\begin{lstlisting}[language=fortran,mathescape=false]
  do i=1, size(names)
     set(i) = nuclide_set(names(i), i)
  enddo
\end{lstlisting}

@@

When creating the library for these four modules, there is a {\tt LIB\_DEFS} 
variable in the makefile that holds the {\tt *\_def.o} file, e.g. 
{\tt utils\_def.o} or {\tt num\_def.o}. This files is never loaded into the 
library as seen below for the {\tt utils} directory. Certain modules have a 
{\tt *\_def.f} file with both definitions and declarations of data that will 
be needed at runtime, so they must be included in the library. Other modules 
have a {\tt *\_def.f} file that contains only definitions and no data 
declarations and therefor only needs to be included at compile time. The Cray 
compiler on Hopper for whatever reason complained that there were undefined 
references to certain {\tt *\_def.o} files. The undefined references only 
occurred for modules whose {\tt *\_def.f} file did not need to be included in 
the library. The fix was to manually include the {\tt *\_def.o} file in the 
library for all of the necessary module directories. The {\tt utils} directory 
is shown here:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

  $(LIB) : $(LIB_DEFS) $(LIB_OBJS)
  	$(LIB_TOOL) $(LIB) $(LIB_OBJS)
\end{lstlisting}
To include the {\tt LIB\_DEFS} file:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

@@

At this point the {\tt install} script in the top {\sf MESA} directory can be 
executed to install {\sf MESA}. This will compile the source code, generate 
the libraries and copy the necessary files to the correct directories. Once, 
{\sf MESA} is installed, {\sf MAESTRO} can be compiled and linked such that 
it can use {\sf MESA}'s EOS and/or network. Make sure the makefile variable 
{\tt COMP} is set to {\tt Cray} so the Cray compiler is used.

>>>>

There are several steps needed to compile {\sf MAESTRO} with {\sf MESA} on 
Hopper:
\begin{enumerate}
\item Download the {\tt MESA} source code using the command described in 
Section \ref{sec:setupmesa}
\item Edit the {\tt makefile\_header} in the {\tt utils} directory
\item Edit the {\tt build\_and\_test} script in the {\tt utils} directory
\item Edit the {\tt chem\_lib.f} file in the {\tt chem} directory
\item Edit the {\tt mtx} makefile
\item Edit the makefiles in {\tt screen}, {\tt utils}, {\tt num} and 
{\tt interp\_1d}
\item Edit the {\tt install} script in the main {\sf MESA} directory
\item Edit the {\tt BoxLib/Tools/F\_mk/GMakedefs.mak} makefile
\item Edit the {\tt BoxLib/Tools/F\_mk/comps/Linux\_cray.mak} file
\item Install {\sf MESA}
\item Compile {\sf MAESTRO}
\end{enumerate}

@@

  # must explicity define all compilation flags
  FCbasic = $(SPECIAL_FC_FLAGS)
  FCimpno = -eI
  FCchecks =
  FCwarn = -m 3
  FCfixed = -f fixed -N 132
  FCfixed72 = -f fixed -N 72
  FCfree = -f free
  FCopt = -O 1
  FCdebug = -g -O0 -R bps
  FCstatic =

@@

The {\tt build\_and\_test} script in the {\tt utils} directory is 
responsible for compiling the main module directory as well as compiling 
and running the test directory. We want to turn off the compiling and 
running of the test directory to ensure that {\sf MESA} compiles successfully 
(it failed to install otherwise). A portion of the {\tt build\_and\_test} 
script looks like this:
\begin{lstlisting}[language=bash,mathescape=false]
  cd make
  make
  check_okay
  cd ../test
  ./mk
  check_okay
  if [ -x test_quietly ]
  then
          ./test_quietly
          check_okay
  fi
  ./ck >& diff.txt
\end{lstlisting}
we wish to change it to this:
\begin{lstlisting}[language=bash,mathescape=false]
  cd make
  make
  check_okay
  #cd ../test
  #./mk
  check_okay
  if [ -x test_quietly ]
  then
  #        ./test_quietly
          check_okay
  fi
  #./ck >& diff.txt
\end{lstlisting}
This disables the compiling and running of the test directory.

@@

Open the {\tt chem\_lib.f} file located in {\tt chem/public}. In the 
{\tt generate\_nuclide\_set} subroutine, the implied do loop must be removed 
and replaced with an actual do loop. For an unknown reason, the implied do 
loop was causing a Segmentation Fault on Hopper with the Cray compiler. The 
implied do loop:
\begin{lstlisting}[language=fortran,mathescape=false]
  set = [(nuclide_set(names(i), i), i=1, size(names))]
\end{lstlisting}
should be changed to an explicit do loop:
\begin{lstlisting}[language=fortran,mathescape=false]
  do i=1, size(names)
     set(i) = nuclide_set(names(i), i)
  enddo
\end{lstlisting}

@@

When creating the library for these four modules, there is a {\tt LIB\_DEFS} 
variable in the makefile that holds the {\tt *\_def.o} file, e.g. 
{\tt utils\_def.o} or {\tt num\_def.o}. This file is never loaded into the 
library as seen below for the {\tt utils} directory. Certain modules have a 
{\tt *\_def.f} file with both definitions and declarations of data that will 
be needed at runtime, so they must be included in the library. Other modules 
have a {\tt *\_def.f} file that contains only definitions and no data 
declarations and therefor only needs to be included at compile time. The Cray 
compiler on Hopper for whatever reason complained that there were undefined 
references to certain {\tt *\_def.o} files. The undefined references only 
occurred for modules whose {\tt *\_def.f} file did not need to be included in 
the library. The fix was to manually include the {\tt *\_def.o} file in the 
library for all of the necessary module directories. The {\tt utils} directory 
is shown here:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

  $(LIB) : $(LIB_DEFS) $(LIB_OBJS)
  	$(LIB_TOOL) $(LIB) $(LIB_OBJS)
\end{lstlisting}
To include the {\tt LIB\_DEFS} file, change the above code to the following:
\begin{lstlisting}[language=make,mathescape=false]
  LIB = libutils.a
  LIB_DEFS = utils_def.o
  LIB_OBJS = $(UTILS_ISNAN).o utils_nan.o utils_dict.o utils_lib.o

@@

At this point the {\tt install} script in the top {\sf MESA} directory can be 
executed to install {\sf MESA}. This will compile the source code, generate 
the libraries and copy the necessary files to the correct directories. Once, 
{\sf MESA} is installed, {\sf MAESTRO} can be compiled and linked such that 
it can use {\sf MESA}'s EOS and/or network. Make sure the makefile variable 
{\tt COMP} is set to {\tt Cray} in the {\sf MAESTRO} problem directory 
so the Cray compiler is used.

### 2012-10-10 Docs/pert_notes/pert.tex
renname docs Docs

\subsubsection{Predicting $\rho'$ at edges}
We define $\rho' = \rho^{(1)} - \rho_0^n$.  Then we predict $\rho'$ to
edges using {\tt make\_edge\_scal} in {\tt density\_advance} and the
underbraced term in Eq.~\ref{rhoprime equation} as the forcing.  This
force is computed in {\tt modify\_scal\_force}.

@@

\subsubsection{Predicting $X_k$ at edges}
\label{sec:pert:predict_X}
Predicting $X_k$ is straightforward.  We convert the cell-centered
$(\rho X_k)$ to $X_k$ by dividing by $\rho$ in each zone and then we
just call {\tt make\_edge\_scal} in {\tt density\_advance} on $X_k$.
The force seen by {\tt make\_edge\_scal} is 0.

@@

\maestro\ solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions,the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T. \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}

@@

The general procedure for making the $(\rho h)$ edge state is as follows:
\begin{enumerate}
\item predict $(\rho h)'$, $h$, or $T$ to the edges (depending on {\tt
  enthalpy\_pred\_type} ) using {\tt make\_edge\_scal} and the forces
  identified in the appropriate evolution equation
  (Eqs.~\ref{rhohprime equation}, \ref{T equation labeled}, or \ref{h
    equation labeled} respectively).

@@

\noindent Note that the various {\tt enthalpy\_pred\_type}s have only been
extensively tested with {\tt species\_pred\_type = 1}.

@@

\begin{table*}[h]
\centering
\caption{Forcing term into {\tt make\_edge\_scal}}
\label{table:pred:hforce}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c}
\hline
\hline
{\tt enthalpy\_pred\_type} &   {advective force} \\
\hline
1 / {\tt predict\_rhohprime} $((\rho h)^\prime)$ &  
 $-(\rho h)^\prime \; \nabla \cdot (\Ubt+w_0 \er) - 
 \nabla \cdot (\Ubt (\rho h)_0) + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T$ \\
2 / {\tt predict\_h}  $(h)$ & $\frac{1}{\rho} \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\
3 / {\tt predict\_T\_then\_rhohprime} $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} \right ] + \nabla \cdot \kth \nabla T \right \}$ \\
4 / {\tt predict\_T\_then\_h}  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\Ubt \cdot \er)
\frac{\partial p_0}{\partial r}\right ] +  \nabla \cdot \kth \nabla T \right\}$ \\
\hline
\end{tabular}
\end{table*}

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
{\tt mkflux} &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\sum(\rho X)_\mathrm{edge} h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\sum(\rho X)_\mathrm{edge} h_\mathrm{edge}$ \\
\hline
\hline
3 / {\tt predict\_rho\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

>>>>

\subsubsection{Predicting $\rho'$ at edges}
We define $\rho' = \rho^{(1)} - \rho_0^n$.  Then we predict $\rho'$ to
edges using {\tt make\_edge\_scal} in {\tt density\_advance} and the
underbraced term in Eq.~\ref{rhoprime equation} as the forcing.  This
force is computed in {\tt modify\_scal\_force}.  This prediction is
done in advective form.

@@

\subsubsection{Predicting $X_k$ at edges}
\label{sec:pert:predict_X}
Predicting $X_k$ is straightforward.  We convert the cell-centered
$(\rho X_k)$ to $X_k$ by dividing by $\rho$ in each zone and then we
just call {\tt make\_edge\_scal} in {\tt density\_advance} on $X_k$.
The force seen by {\tt make\_edge\_scal} is 0.  The prediction is
done in advective form.

@@

\maestro\ solves an enthalpy equation.  
The full enthalpy equation is
\begin{eqnarray}
\frac{\partial(\rho h)}{\partial t} &=& -\nabla\cdot(\rho h \Ub) + \frac{Dp_0}{Dt} 
+ \nabla\cdot \kth \nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext} \nonumber \\
&=& \underbrace{-\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub}_{-\nabla\cdot(\rho h\Ub)} 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r}}_{\frac{Dp_0}{Dt}} 
+ \nabla\cdot\kth\nabla T + \rho H_{\rm nuc} + \rho H_{\rm ext}.
\end{eqnarray}
%The full temperature equation is
%\begin{equation}
%\frac{\partial T}{\partial t} = -\Ub\cdot\nabla T
%+ \frac{1}{\rho c_p}\left\{(1-\rho h_p)\left[\psi
%+ (\Ubt \cdot \er )\frac{\partial p_0}{\partial r}\right] - \sum_k\rho\xi_k\dot\omega_k 
%+ \rho H_{\rm nuc} + \rho H_{\rm ext}\right\}.
%\end{equation}
Due to Strang-splitting of the reactions, the call to {\tt
  react\_state} has already been made.  Hence, the goal is to compute
an edge state enthalpy starting from $(\rho h)^{(1)}$ using an
enthalpy equation that does not include the $\rho H_{\rm nuc}$ and
$\rho H_{\rm ext}$ terms, where were already accounted for in {\tt
  react\_state}, so our equation becomes
\begin{equation}
\frac{\partial(\rho h)}{\partial t} = -\Ub\cdot\nabla(\rho h) - \rho h\nabla\cdot\Ub 
+ \underbrace{\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla\cdot\kth\nabla T}_{``(\rho h) ~ \text{force}"} \label{rhoh equation}
\end{equation}
We define the base state enthalpy evolution equation as
\begin{eqnarray}
\frac{\partial(\rho h)_0}{\partial t} &=& -\nabla\cdot[(\rho h)_0 w_0\eb_r] 
+ \frac{D_0p_0}{Dt} \nonumber \\
&=& -w_0\frac{\partial(\rho h)_0}{\partial r} 
- \underbrace{(\rho h)_0\frac{\partial w_0}{\partial r}+ \psi}_{``(\rho h)_0 ~ \text{force}"}
\enskip .\label{rhoh0 equation}
\end{eqnarray}

@@

The general procedure for making the $(\rho h)$ edge state is as follows:
\begin{enumerate}
\item predict $(rho h)$, $(\rho h)'$, $h$, or $T$ to the edges (depending on {\tt
  enthalpy\_pred\_type} ) using {\tt make\_edge\_scal} and the forces
  identified in the appropriate evolution equation
  (Eqs.~\ref{rhohprime equation}, \ref{T equation labeled}, or \ref{h
    equation labeled} respectively).

@@

@@

\begin{table*}[h]
\centering
\caption{Forcing term into {\tt make\_edge\_scal}}
\label{table:pred:hforce}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{l|c}
\hline
\hline
{\tt enthalpy\_pred\_type} &   {advective force} \\
\hline
0 / {\tt predict\_rhoh}  $(\rho h)$ & $ \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\
1 / {\tt predict\_rhohprime} $((\rho h)^\prime)$ &  
 $-(\rho h)^\prime \; \nabla \cdot (\Ubt+w_0 \er) - 
 \nabla \cdot (\Ubt (\rho h)_0) + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T$ \\
2 / {\tt predict\_h}  $(h)$ & $\frac{1}{\rho} \left [\psi + (\Ubt \cdot \er)
  \frac{\partial p_0}{\partial r} + \nabla \cdot \kth \nabla T \right ]$ \\
3 / {\tt predict\_T\_then\_rhohprime} $(T)$ & $\frac{1}{\rho c_p} \left \{ (1 - \rho h_p) 
   \left [\psi + (\Ubt \cdot \er) \frac{\partial p_0}{\partial r} \right ] + \nabla \cdot \kth \nabla T \right \}$ \\
4 / {\tt predict\_T\_then\_h}  $(T)$ & $\frac{1}{\rho c_p} \left\{ (1 - \rho h_p) \left [\psi + (\Ubt \cdot \er)
\frac{\partial p_0}{\partial r}\right ] +  \nabla \cdot \kth \nabla T \right\}$ \\
\hline
\end{tabular}
\end{table*}

\begin{landscape}
\begin{table}[t]
\caption{Summary of enthalpy edge state construction}
\label{table:pred:hoverview}
\renewcommand{\arraystretch}{1.5}
{\small
\centering
\begin{tabular}{l|l|c|c|c|c}
\hline
\hline
{\tt species\_pred\_type} &   
{\tt enthalpy\_pred\_type} &
{cell-centered} &
{intermediate} &
{species quantity} &
{final $(\rho h)$} \\[-5pt]
 &
 &
{quantity predicted} &
{``enthalpy''} &
{available in} &
{edge state} \\[-5pt]
 &
 &
{in {\tt make\_edge\_scal}} &
{edge state} &
{\tt mkflux} &
 \\
\hline 
1 / {\tt predict\_rhoprime\_and\_X}  & 0 / {\tt predict\_rhoh} &
  $(\rho h)$ & $(\rho h)_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $(\rho h)_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
1 / {\tt predict\_rhoprime\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho'_\mathrm{edge}$ & 
  $\left ( \rho_0^{n+\myhalf,{\rm avg}} + \rho'_\mathrm{edge} \right ) h_\mathrm{edge}$ \\
\hline
\hline
2 / {\tt predict\_rhoX}  & 0 / {\tt predict\_rhoh} &
  $(\rho h)$ & $(\rho h)_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $(\rho h)_\mathrm{edge}$ \\
2 / {\tt predict\_rhoX}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\sum(\rho X)_\mathrm{edge} h_\mathrm{edge}$ \\
2 / {\tt predict\_rhoX}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
2 / {\tt predict\_rhoX}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $(\rho X)_\mathrm{edge}$, $\sum(\rho X)_\mathrm{edge}$ & 
  $\sum(\rho X)_\mathrm{edge} h_\mathrm{edge}$ \\
\hline
\hline
3 / {\tt predict\_rho\_and\_X}  & 0 / {\tt predict\_rhoh} &
  $(\rho h)$ & $(\rho h)_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $(\rho h)_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  & 1 / {\tt predict\_rhohprime} &
  $(\rho h)'$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 2 / {\tt predict\_h} &
  $h$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
3 / {\tt predict\_rho\_and\_X}  & 3 / {\tt predict\_T\_then\_rhohprime} &
  $T$ & $(\rho h)'_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\left [ (\rho h)_0^{n+\myhalf,{\rm avg}} + (\rho h)'_\mathrm{edge} \right ]$ \\
3 / {\tt predict\_rho\_and\_X}  & 4 / {\tt predict\_T\_then\_h} &
  $T$ & $h_\mathrm{edge}$ & 
  $X_\mathrm{edge}$, $\rho_\mathrm{edge}$ & 
  $\rho_\mathrm{edge} h_\mathrm{edge}$ \\
\hline
\end{tabular}
} % end \small
\end{table}
\end{landscape}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Method 0: {\tt enthalpy\_pred\_type} = {\tt predict\_rhoh}}

Here we wish to construct $(\rho h)_\mathrm{edge}$ by predicting
$(\rho h)$ to the edges directly.  We use {\tt make\_edge\_scal} with
{\tt is\_conservative = .true.} on $(\rho h)$, with the underbraced term
in Eq.~\ref{rhoh equation} as the force (computed in {\tt mkrhohforce}).

### 2012-10-10 Docs/test_suite/test_suite.tex
renname docs Docs

An automated regression test suite for \maestro\ (or any BoxLib-based
code) written in Python exists in {\tt BoxLib/Tools/C\_util/regtests/}
as {\tt testnew.py}.  The test suite consists of a set of problem
definitions (the \maestro\ problem + their inputs file, etc.).  When
the suite is run the first time, the plotfiles created at the end of
each problem's execution is stored as a benchmark.  After this
initialization, each subsequent run of the test suite compares the
current output of the code, level-by-level and zone-by-zone to the
stored benchmarks (using the {\tt fcompare.f90} routine in {\tt
  AmrPostprocessing/F\_Src/}).  Any differences are flagged as errors.
A web page report is generated by the test suite and provides a
history of the regression testing.  Single-processor and parallel test
problems, compilation tests, self-tests (problems that determine by
themselves whether they were successfully), and testing restarting
from a checkpoint file are supported.

>>>>

An automated regression test suite for \maestro\ (or any BoxLib-based
code) written in Python exists in {\tt BoxLib/Tools/RegressionTesting/}
as {\tt testnew.py}.  The test suite consists of a set of problem
definitions (the \maestro\ problem + their inputs file, etc.).  When
the suite is run the first time, the plotfiles created at the end of
each problem's execution is stored as a benchmark.  After this
initialization, each subsequent run of the test suite compares the
current output of the code, level-by-level and zone-by-zone to the
stored benchmarks (using the {\tt fcompare.f90} routine in {\tt
  AmrPostprocessing/F\_Src/}).  Any differences are flagged as errors.
A web page report is generated by the test suite and provides a
history of the regression testing.  Single-processor and parallel test
problems, compilation tests, self-tests (problems that determine by
themselves whether they were successfully), and testing restarting
from a checkpoint file are supported.
